Untitled

### 2017-08-21 PaperCode.Rmd
upgrade
Code clean up and also, modelling to allow the whole of England to be predicted.

@@

@@

@@

setwd(file.path(RegionsComp, "Region North East"))
list.files()
#Not sure all are there ask for confirmation
# SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
#   StructureData(lowuse = c(2:4,6,8:10))

@@

@@

z<- MakeLeaflet(DurhamDATA)
z
# 
setwd(basewd)
 saveWidget(z, file=file.path(basewd, "RBKC&Westminster.html"), selfcontained = TRUE )

@@

@@

#ExO excluding Other
#A only A type sales
#B only Btype sales

# #load full data
# BootStrapRES <-LoadAddDistribCompare("BootStrapRES.rds")
# 
# #Include only full price standard purchases
# BootStrapRESA <-LoadAddDistribCompare("BootStrapRES_A.rds", type = "A")
# 
# #Inlcude only transfers and Buy-to-let and purcheses to non-private individuals
# BootStrapRESB <-LoadAddDistribCompare("BootStrapRES_B.rds", type = "B")

#Repeat excluding all the properties classed as other
setwd(basewd)
BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                         PropertyTypes = c("D", "S", "T", "F"))
# 
# BootStrapRESExOA <-LoadAddDistribCompare("BootStrapRESExOA.rds", type = "A", 
#                                          PropertyTypes = c("D", "S", "T", "F"))
# 
# BootStrapRESExOB <-LoadAddDistribCompare("BootStrapRESExOB.rds", type = "B", 
#                                          PropertyTypes = c("D", "S", "T", "F"))

@@

ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~get(.x) %>%ncol))==4]

#saveRDS(BootStrapRESExO, file = "BootStrapRESExO.rds")

@@

land registry 
sue gambles

#gets the list of LADs we currently have data for in alphabetical order so they can be joined to the combine
CurrentLADS <- ls(pattern = "DATA") %>%
  map_chr(~{df<- get(.x)
  df <- df %>%
  group_by(LAD11CD) %>%
  summarise(count = n())
df$LAD11CD[which.max(df$count)]}
)

#check any that are accidently not processed
ls(pattern = "DATA")[(ls(pattern = "DATA") %>% map_dbl(~.x %>% get %>% ncol))<10]

Combine1 <- BootResSummaryData(BootStrapRES) %>% mutate(LAD11CD = CurrentLADS)

Combine2 <- BootResSummaryData(BootStrapRESA) %>% mutate(LAD11CD = CurrentLADS)

Combine3 <- BootResSummaryData(BootStrapRESB) %>% mutate(LAD11CD = CurrentLADS)

#Excluding Other
Combine1ExO <- BootResSummaryData(BootStrapRESExO) %>% mutate(LAD11CD = CurrentLADS)

Combine2ExO <- BootResSummaryData(BootStrapRESExOA) %>% mutate(LAD11CD = CurrentLADS)

Combine3ExO <- BootResSummaryData(BootStrapRESExOB) %>% mutate(LAD11CD = CurrentLADS)

@@

ABratio <- prices %>% 
  filter(X5 %in% PropertyTypes) %>%
  group_by(Admin_district_code, X15) %>%
  summarise(count = n(), 
            mean = mean(X2)) %>%
  rename(LAD11CD = Admin_district_code)

ABratio2 <- ABratio%>%
  select(-mean) %>%
spread(key = X15, value = count) %>%
  mutate(Countratio = B/(A+B))

ABratio3 <- ABratio%>%
  select(-count) %>%
spread(key = X15, value = mean) %>%
  mutate(Valueratio = B/(A))

ABratio4 <-  left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
  left_join(LADNMs) %>%
  left_join(prices %>% 
  group_by(Admin_district_code) %>%
summarise(mean = mean(X2)) %>%
  rename(LAD11CD = Admin_district_code))

CombineAB <- Combine1ExO %>% 
  left_join(ABratio4, by = "LAD11CD")

@@

#Inlcuding deprivation
```{r}
setwd(file.path(basewd, "Deprivation"))
list.files()
LADDep<-read_excel("File_10_ID2015_Local_Authority_District_Summaries.xlsx", sheet = 2) %>%
  setNames(make.names(names(.)) %>% gsub("IMD...", "",.) %>% trimws ) %>%
  rename(LAD11CD = Local.Authority.District.code..2013.)

LSOADomDep<-read_excel("File_2_ID_2015_Domains_of_deprivation.xlsx" , sheet = 2) %>%
  setNames(make.names(names(.))) %>%
  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
  rename(LAD11CD = Local.Authority.District.code..2013.)

LSOADep<-read_excel("File_1_ID_2015_Index_of_Multiple_Deprivation.xlsx", sheet = 2) %>%
  setNames(make.names(names(.))) %>%
  setNames(make.names(names(.)) %>% gsub("Index.of.Multiple.Deprivation..IMD..", "",.) %>% trimws ) %>%
  rename(LAD11CD = Local.Authority.District.code..2013.,
         LSOA_CODE = LSOA.code..2011.)

CombineAB <- CombineAB %>% left_join(LADDep, by = "LAD11CD")

CombineAB %>%
  ggplot(.,aes(x= diffPerc, y = Ttest.p.value, color =Rank.of.extent<100)) + geom_jitter()

@@

Combine1ExO2 <- CombineAB%>%
  mutate(LUPdepExt)

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
  geom_jitter()

Combine1ExO2 %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
  geom_jitter()

@@

```{r}
LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(meandiff = price-mean(price),
         pricepercent = percent_rank(price))

ModelMe <- Combine1ExO2 %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  #filter out wales
  filter(!grepl("W", LAD11CD))%>%
  select(LAD, absdiff, LUPdepExt, Extent, maxPerc,Ttest.p.value, pricepercent) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc))

@@

library(rpart)
library(caret)

#classification
#three models
svm.model <- svm(Reference~ pricepercent +LUPdepExt+ maxPerc, ModelMe)
rpart.model <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, ModelMe)
Binom <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, family=binomial(link='logit'),data=ModelMe)

linear.model <- lm(absdiff~ LUPdepExt + maxPerc+ pricepercent,data=ModelMe)

confusionMatrix(predict(svm.model, ModelMe, type = "class"), ModelMe$Reference) %>% unlist
confusionMatrix( predict(rpart.model, ModelMe, type = "class"), ModelMe$Reference)
confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)

predict(linear.model, ModelMe)
summary(linear.model)
```

@@

set.seed(1983)
test <- 1:1000 %>% map_df(~{
TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

rpart.model2 <- rpart(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))

Confmat <- confusionMatrix( predict(rpart.model2, as.data.frame(TestResample$test), type = "class"), as.data.frame(TestResample$test)$Reference)

Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

test %>% ggplot(., aes(x= Accuracy)) +geom_density()

test %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

t.test(test$Accuracy, test$AccuracyNull, alternative = "greater")

set.seed(1983)
test2 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- svm(Reference ~pricepercent +LUPdepExt+ maxPerc, as.data.frame(TestResample$train))

  Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "class"),
                              as.data.frame(TestResample$test)$Reference)

  Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
          Confmat$byClass %>% as.matrix %>%t %>% data.frame) %>%
  mutate(ID = .x)

test2 %>% ggplot(., aes(x= Accuracy)) +geom_density()

test2 %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

t.test(test2$Accuracy, test2$AccuracyNull, alternative = "greater")

@@

set.seed(1983)
test3 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + maxPerc+ pricepercent, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

@@

test3 %>% ggplot(., aes(x= Accuracy)) +geom_density()

test3 %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

t.test(test3$Accuracy, test3$AccuracyNull, alternative = "greater")

# 
# set.seed(1983)
# test4 <- 1:1000 %>% map_df(~{
#   TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))
# 
#   model <- glm(Reference~ LUPdepExt + maxPerc+ priceRatio, 
#                family=binomial(link='logit'),
#                as.data.frame(TestResample$train))
# 
#   Confmat <- confusionMatrix( predict(model, as.data.frame(TestResample$test), type = "response")>0.5,
#                               as.data.frame(TestResample$test)$Reference) 
# 
#   Out<- bind_cols(Confmat$overall %>% as.matrix %>%t %>% data.frame,
#           Confmat$byClass %>% as.matrix %>%t %>% data.frame,
#           coefficients(model)%>% as.matrix %>%t %>% data.frame) %>%
#   mutate(ID = .x)
# 
# }
# )
# 
# test4 %>% ggplot(., aes(x= Accuracy)) +geom_density()
# 
# test4 %>%
#   mutate(diff = Accuracy - AccuracyNull) %>% 
#   ggplot(., aes(x= diff)) +geom_density()
# 
# t.test(test4$Accuracy, test4$AccuracyNull, alternative = "greater")
# 
# 
# t.test(test3$Accuracy- test3$AccuracyNull, test4$Accuracy - test4$AccuracyNull, alternative = "greater")

@@

>>>>

AllerdaleCUMBRIADATA <- read_excel("F17.132_Copy of Allerdale discounts LSOA_170815.xlsx"  , sheet=1)[1:4] %>%  
  StructureData(c(4:10))

@@

#Bristol appears to have not included second homes
#BristolDATA <- read_excel("Bristol%2c City ofDiscountsLSOA_as at 110817.xlsx")[c(1:4)] %>%
#  StructureData()

@@

CalderdaleDATA <- read_excel("Copy of CalderdaleDiscountsLSOA.xlsx" )[,1:4]%>%
  StructureData(c(7,10,22:25))

BradfordDATA <- read_excel("Copy of BradfordDiscountsLSOA.xlsx")[1:4] %>%
  StructureData(c(2:7))

RichmondshireDATA <- read_excel("Richmondshire FOI 4960.xls", col_names = FALSE)[1:2] %>%
    setNames(c("Exemption.type", "Postcode")) %>%
  mutate(Postcode = sub(" ", "", Postcode)) %>%
  left_join(., PstCdLSOA.raw,  by=c("Postcode") ) %>%
  rename(LSOA_CODE = lsoa11cd) %>%
  select(Exemption.type, LSOA_CODE, Postcode, Country_code) %>%
  StructureData(lowuse = c(2:7))

@@

setwd(file.path(RegionsComp, "Region North East"))
list.files()
#Not sure all are there ask for confirmation
 SunderlandDATA <- read_excel("Sunderland Freedom of Informaton Request from Jonathan Bourne- 17-07-21-Discounts.xlsx"  , sheet=1)%>% .[,1:4] %>%
   StructureData(lowuse = c(2:4,6,8:10))

@@

HaveringLONDATA <- read_excel("AIR12965P Informatiion provided by Council Tax.xlsx" ) %>%
  rename(DiscClass = X__1) %>%
  select(-Mawneys, -`Aveley & Uplands`, -Whalebone) %>%
  gather(key = "ward", value = "counts", -DiscClass) %>%
  spread(key= DiscClass, value = counts, fill = 0) %>%
  mutate(Empty = rowSums(.[,c(5:6,14,17)]), LowUse = Empty+ `Second Home Class A`+ `Second Homes Class B`) %>% 
  bind_cols(., wardnames %>% filter(grepl("Havering", LAD11NM))) %>%
  SemiDataStructure

@@

z<- MakeLeaflet(AllerdaleDATA)
z
# 
setwd(basewd)
 saveWidget(z, file=file.path(basewd, "Cumbria.html"), selfcontained = TRUE )

@@

BradfordDATA %>% filter(LAD11NM=="Bradford") %>%
  MakeLeaflet

@@

BootStrapRESExO <-LoadAddDistribCompare("BootStrapRESExO.rds", 
                                         PropertyTypes = c("D", "S", "T", "F"))

@@

#Make a summary dataframe
Combine1ExO <- BootResSummaryData(BootStrapRESExO) 
```

@@

@@

#calulcate the number of properties sold and the mean price
ABratio <- prices %>% 
  filter(X5 %in% PropertyTypes) %>%
  group_by(Admin_district_code, X15) %>%
  summarise(count = n(), 
            mean = mean(X2)) %>%
  rename(LAD11CD = Admin_district_code)

ABratio2 <- ABratio%>%
  select(-mean) %>%
spread(key = X15, value = count) %>%
  mutate(Countratio = B/(A+B)) %>%
  rename(CountofA = A, CountofB = B)

ABratio3 <- ABratio%>%
  select(-count) %>%
spread(key = X15, value = mean) %>%
  mutate(Valueratio = B/(A)) %>%
  rename(MeanofA= A, MeanofB = B)

CombineAB <-left_join(ABratio2, ABratio3, by = "LAD11CD") %>%
  left_join(Combine1ExO, ., by = "LAD11CD")

rm(ABratio); rm(ABratio2); rm(ABratio3)

@@

#Inlcuding deprivation
```{r}

@@

#Add in deprivation
Combine1ExO <- select(LADDep, LAD11CD ,Extent) %>% 
  left_join(CombineAB, ., by = "LAD11CD") %>%
  mutate(LUPdepExt)

Combine1ExO %>% ggplot(.,aes(x= maxPerc, y = LUPdepExt, colour = absdiff>0)) +
  geom_jitter()

Combine1ExO %>% ggplot(.,aes(x= maxPerc, y =Ttest.p.value, colour = LUPdepExt>0.10)) +
  geom_jitter()

@@

```{r}
LADprice <- prices %>%
  filter(X5!= "O") %>%
  group_by(Admin_district_code) %>%
summarise(price = mean(X2)) %>%
  mutate(pricepercent = percent_rank(price))

ModelMe <- Combine1ExO %>%
  left_join(LADprice, by = c("LAD11CD"="Admin_district_code"))%>%
  left_join(Vacants, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes,
         LTVPerc = Vacants/Homes) %>%
  #filter out wales
  filter(!grepl("W", LAD11CD)) %>%
#  select(LAD, absdiff, LUPdepExt,  maxPerc,Ttest.p.value, pricepercent) %>%
  mutate(Reference = as.factor(absdiff>0) ) %>%
  #scaled so that the binomial can be interpreted
  mutate(pricepercent = scale(pricepercent),
         LUPdepExt = scale(LUPdepExt),
         maxPerc = scale(maxPerc))

@@

rowsum(.)>5 ~TRUE
#classification

#LUPdepExt and Pricepercent are the only useful ones really
Binom <- glm(Reference~ LUPdepExt +LADPerc +maxPerc+ mean.y, family=binomial(link='logit'),data=ModelMe)

Binom <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)

confusionMatrix(predict(Binom, ModelMe, type = "response")>0.5 , ModelMe$Reference)

test <- lm(Percdiff ~ LUPdepExt +LADPerc +maxPerc+ mean.y, data = ModelMe)

summary(test)

summary(Binom)

coef(Binom) %>% as.data.frame
```

@@

@@

set.seed(1983)
ModelStats <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

@@

ModelStats %>% ggplot(., aes(x= Accuracy)) +geom_density()

ModelStats %>%
  mutate(diff = Accuracy - AccuracyNull) %>% 
  ggplot(., aes(x= diff)) +geom_density()

ModelStats %>% ggplot(., aes(x= AccuracyPValue)) +geom_density()
ModelStats %>% ggplot(., aes(x= Kappa)) +geom_density()

t.test(ModelStats$Accuracy, ModelStats$AccuracyNull, alternative = "greater")

test <- ModelStats %>% 
  select( X.Intercept., LUPdepExt, maxPerc, pricepercent) %>%
  gather

test %>% ggplot(.,aes(x = key, y = value, fill = key)) + geom_boxplot() + 
  labs(title = "Direction each variable pushes the outcome")

test %>% ggplot(.,aes(x = value, fill = key)) + geom_density( alpha = 0.5)

@@

```{r}
set.seed(1983)
ModelStats2 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ Extent + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

set.seed(1983)
ModelStats3 <- 1:1000 %>% map_df(~{
  TestResample <- resample_partition(ModelMe, c(test = 0.3, train = 0.7))

  model <- glm(Reference~ LUPdepExt + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample$train))

Outcome <- bind_rows(data_frame(model = "generic", Accuracy = ModelStats2$Accuracy), 
data_frame(model = "cutsom", Accuracy = ModelStats3$Accuracy) )

Outcome %>%
  ggplot(.,aes(x = Accuracy, fill = model)) + geom_density(alpha = 0.3)

#The model that uses easily available data is 3% less accurate than the other model.
t.test(ModelStats2$Accuracy, ModelStats1$Accuracy)

cor(ModelMe$Vacants, ModelMe$VacantsPerc)

cor(ModelMe$Vacants, ModelMe$LTV)
cor(ModelMe$VacantsPerc, ModelMe$LTVPerc)

interpreting the coefficients of the model shows us that there is a natural tendency for LUPs to be more expensive than regular housing, the probability of them being more expensive increases if the local authority is already expensive compared to the rest of the local authorities. In addition the greater the maximum concentration of LUPs also increase the probability of them being more expensive than regular housing. However if the LUPs are generally in deprived areas then the probability of them being more expensive than regular housing decreases.

Using the models produced in the previous section I can now predict areas where primary purchases are being out competed across the England

set.seed(1983)
MultiCheck <- 1:21 %>% map(~{
  TestResample <- resample_bootstrap(ModelMe)

  model <- glm(Reference~ Extent + price + VacantsPerc, 
               family=binomial(link='logit'),
               as.data.frame(TestResample))

  data_frame(x = predict(model, ModelMe, type = "response")>0.5) %>%
    setNames(paste("Model", .x, sep="_"))
}
) %>% bind_cols() %>% mutate(
  Outcome = case_when(
  rowSums(.)>ncol(.)/2 ~TRUE,
  rowSums(.)<=ncol(.)/2 ~FALSE
))

test <- ModelMe %>%
  bind_cols(., select(MultiCheck, Outcome)) %>%
  mutate(Correct = Reference == Outcome) %>%
  filter(!Correct) %>%
  select(LAD, Reference, Outcome)

confusionMatrix(MultiCheck$Outcome, ModelMe$Reference)

BinomSimp <- glm(Reference~ price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)

BinomExtent <- glm(Reference~ Extent + price + VacantsPerc, family=binomial(link='logit'),data=ModelMe)
rpartExtent <- rpart(Reference~ Extent + price + VacantsPerc,data=ModelMe)

confusionMatrix(predict(BinomSimp, ModelMe, type = "response")>0.5 , ModelMe$Reference)

confusionMatrix((predict(BinomExtent, ModelMe, type = "response")>0.5) , ModelMe$Reference)
confusionMatrix(predict(rpartExtent, ModelMe, type = "prob")[,2] , ModelMe$Reference)

LadHomes <-  EW2 %>%
  group_by(LAD11CD) %>%
  summarise(Homes = sum(Homes, na.rm = TRUE),
            Pop = sum(Pop, na.rm = TRUE))

tol <- 0

#random forest appears better than multilinear but when checked on many resamples it is worse... how? To much noise?
EnglandComp <- LADDep %>% 
  select (LAD11CD, LAD11NM = Local.Authority.District.name..2013., Extent)%>% 
  left_join(., Vacants, by = "LAD11CD") %>%
  left_join(LADprice, by = c("LAD11CD" = "Admin_district_code")) %>%
  left_join( LadHomes, by = "LAD11CD") %>%
  mutate(VacantsPerc = Vacants/Homes) %>%
  mutate(Significant.Competition = predict(BinomExtent, ., type = "response")) %>%
  mutate(Comp.Type = case_when(
    .$Significant.Competition<0.5-tol ~"No",
    .$Significant.Competition>0.5 + tol ~"Yes",
    .$Significant.Competition>0.5-tol & .$Significant.Competition<0.5+tol ~"Borderline"
  ))

EnglandComp %>%
  ggplot(aes(x = Comp.Type, y= price, fill = Comp.Type)) + geom_boxplot()

EnglandComp %>%
  group_by(Comp.Type) %>%
  summarise(mean = mean(price),
            median = median(price),
            Homes = sum(Homes),
            Pop = sum(Pop)) %>%
  mutate(HomesPerc = Homes/sum(Homes),
         PopPerc = Pop/sum(Pop))

test <-ls(pattern = "DATA") %>%
  map_df(~get(.x) %>%
           group_by(LAD11CD) %>%
           mutate(LowUsePercentile = percent_rank(LowUsePerc),
                  MeanPricePercentile = percent_rank(MeanPrice)))

cor(test$LowUsePerc,test$MeanPrice,"complete.obs")
cor(test$LowUsePerc,test$MedianPrice, "complete.obs")

cor(test$LowUsePercentile,test$MeanPricePercentile , "complete.obs")

test %>%
  ggplot(aes(x= LowUsePercentile, y = MeanPricePercentile)) +geom_point()

test <-ls(pattern = "DATA") %>%
  map_dbl(~{ df <-get(.x)
    cor(df$LowUsePerc,df$MeanPrice,"complete.obs", method = "kendall")
  })

  plot(density(abs(test)))

  Combine1ExO %>%
    ggplot(., aes(x = absdiff>0 )) +geom_bar()

### 2017-08-21 testCode.Rmd
upgrade
Code clean up and also, modelling to allow the whole of England to be predicted.

CalcLowUse<- function(df){ 
  df %>%
  select(LSOA_CODE, LowUse) %>%
        left_join(., EW2, by = c("LSOA_CODE" = "ECODE")) %>% 
        group_by(Admin_ward_code)  %>%
        mutate(LowUsePerc = round(LowUse/Homes *100), 
               WardLowUse = sum(LowUse) ,
               WardLowUsePerc = round(WardLowUse/sum(Homes)*100)) %>% 
        ungroup %>% 
        left_join(., MeanWardPrice, by = "Admin_ward_code") %>% 
        mutate(ValLow = LowUse*MeanPrice,
               LowuseClass = cut(LowUsePerc, c(-1,10,20, 30,100), 
                                 labels =  c("0-10","11-20","21-30", "30+")),
               WardLowuseClass = cut(WardLowUsePerc, c(0,10,20, 30, 100), 
                                     labels = c("0-10","11-20","21-30", "30+")) )
}

@@

test <- ls(pattern = "LON") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

@@

test <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA) %>%
  map_df(~.x) %>%   
  group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

z

@@

>>>>

CombineLowUse<- function(df){ 
  df %>%
  select(LSOA_CODE, LowUse) %>%
    CalcLowUse()

}

@@

test <- ls(pattern = "CUMBRIA") %>% 
  map_df(~get(.x)) %>%
   group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

@@

testTower <- TowerLONDATA %>%
  CalcLowUse()

test2 <- ls(pattern = "LON") %>%
  map_df(~get(.x)) %>%   
  group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

test2 <-list( WestminsterLONDATA, ChelseaLONDATA, CoLLONDATA, CamdenLONDATA, TowerLONDATA) %>%
  map_df(~.x) %>%   
  group_by(LSOA_CODE) %>%
   summarise(LowUse = sum(LowUse, na.rm = TRUE)) %>% 
  CalcLowUse()

y<- MakeLeaflet(test2)

y

y2<- MakeLeaflet(TowerLONDATA)

y2

@@

SalesLAD <- prices %>%
  group_by(Admin_district_code) %>%
    filter(X5 %in% c("D", "S", "T", "F")) %>%
    summarise(sales = n(), 
            mean = mean(X2, na.tm = TRUE))

SalesWard <- prices %>%
  group_by(Admin_ward_code) %>%
    filter(X5 %in% c("D", "S", "T", "F")) %>%
    summarise(sales = n(), 
            mean = mean(X2, na.tm = TRUE))

SalesWard %>% ggplot(aes(x = sales, y = mean )) + geom_point()

```{r}
test <- ChelseaLONDATA %>%
            # select(WardLowUsePerc, WardLowUse) %>%
             mutate( WardLowUsePerc = ifelse(is.na(WardLowUsePerc),0, WardLowUsePerc)) %>%
             summarise( maxPerc = max(WardLowUsePerc, na.rm=TRUE),
                        minPerc = min(WardLowUsePerc, na.rm=TRUE),
                        diffPerc = maxPerc-minPerc,
                        max = max(WardLowUse, na.rm=TRUE),
                        min = min(WardLowUse, na.rm=TRUE),
                        diff = max-min,
                        mean = mean(WardLowUse, na.rm=TRUE),
                        median = median(WardLowUse, na.rm=TRUE),
                        LAD = sub("DATA", "", "ChelseaLONDATA"),
                        TurnoverPerc = sum(PercTurnover*Homes, na.rm = TRUE)/sum(Homes, na.rm = TRUE),
                        LUPTurnoverPerc = sum(PercTurnover*LowUse, na.rm = TRUE)/sum(LowUse, na.rm = TRUE)
                        )
```
